---
title: "Joining Datasets in R"
author: "Kaitlyn Elliott"
date: "12/24/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
 
# Reading in Datasets and Libraries 
```{r}
library(tidyverse)
library(lubridate)
library(sf)
library(rgdal)
library(sp)
library(rgeos)
library(tidyr)
library(plyr)



# Delininated BMPs from ArcGIS Pro

tr104_bmp_deliniated <- st_read(file.path("./Input_Files/deliniate_tr104.shp"))
tr104_bmp_deliniated <- st_transform(tr104_bmp_deliniated, 2248)
tr109_bmp_deliniated <-st_read(file.path("./Input_Files/deliniate_tr109.shp"))
tr109_bmp_deliniated <- st_transform(tr109_bmp_deliniated, 2248)
tr109_bmp_deliniated$Area_m2 <- "NA"
cr_bmp_deliniated <- st_read(file.path("./Input_Files/deliniate_cr.shp"))
cr_bmp_deliniated <- st_transform(cr_bmp_deliniated, 2248)
cb_bmp_deliniated <- st_read(file.path("./Input_Files/deliniate_cb.shp"))
cb_bmp_deliniated <- st_transform(cb_bmp_deliniated, 2248)
sb_bmp_deliniated <- st_read(file.path("./Input_Files/deliniate_sb.shp"))
sb_bmp_deliniated <- st_transform(sb_bmp_deliniated, 2248)


# Landcover Datasets

lulc_2019 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2019_poly.shp"))
lulc_2019 <- st_transform(lulc_2019, 2248)

lulc_2018 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2018_poly.shp"))
lulc_2018 <- st_transform(lulc_2018, 2248)

lulc_2017 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2017_poly.shp"))
lulc_2017 <- st_transform(lulc_2017, 2248)

lulc_2016 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2016_poly.shp"))
lulc_2016 <- st_transform(lulc_2016, 2248)

lulc_2015 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2015_poly.shp"))
lulc_2015 <- st_transform(lulc_2015, 2248)

lulc_2014 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2014_poly.shp"))
lulc_2014 <- st_transform(lulc_2014, 2248)

lulc_2013 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2013_poly.shp"))
lulc_2013 <- st_transform(lulc_2013, 2248)

lulc_2012 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2012_poly.shp"))
lulc_2012 <- st_transform(lulc_2012, 2248)

lulc_2011 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2011_poly.shp"))
lulc_2011 <- st_transform(lulc_2011, 2248)

lulc_2010 <- st_read(file.path("./Input_Files/poly_planet_lulc/lulc_2010_poly.shp"))
lulc_2010 <- st_transform(lulc_2010, 2248)


# BMP Information as point data

stormwater_tr109 <- st_read(file.path("./Input_Files/stormwater_tr109.shp"))
stormwater_tr109 <- st_transform(stormwater_tr109, 2248) 
stormwater_tr104 <- st_read(file.path("./Input_Files/stormwater_tr104.shp")) 
stormwater_tr104 <- st_transform(stormwater_tr104, 2248)
stormwater_tr104 <- stormwater_tr104[,c(1:32,107)]
stormwater_cr <- st_read(file.path("./Input_Files/stormwater_cr.shp")) 
stormwater_cr <- st_transform(stormwater_cr, 2248)
stormwater_cb <- st_read(file.path("./Input_Files/stormwater_cb.shp")) 
stormwater_cb <- st_transform(stormwater_cb, 2248)
stormwater_sb <- st_read(file.path("./Input_Files/stormwater_sb.shp")) 
stormwater_sb <- st_transform(stormwater_sb, 2248)

# Storage information for BMPs

bmp_full <- read.csv("./Input_Files/BMP_2020_COMPARE.csv")
new_stores <- read.csv("./Input_Files/full_SEQNO_missing_stores_cf_bmp.csv")

new_stores$Stores_cf <- new_stores$Stores
new_stores$STRUC_DTAL <- new_stores$STRUC_DTAL.x

bmp_full$Stores_cf <- as.numeric(bmp_full$Stores_cf)

bmp_full <- full_join(bmp_full, new_stores) 

bmp_full <- bmp_full %>%
  filter(is.na(ASSET)==FALSE)%>%
  dplyr::select(ASSET, Stores_cf)

# Basin boundaries

tr109 <- st_read(file.path("./Input_Files/tr109_basin.shp")) 
tr109 <- st_transform(tr109, 2248)

tr104 <- st_read(file.path("./Input_Files/tr104_basin.shp"))
tr104 <- st_transform(tr104, 2248)

cabin_branch <- st_read(file.path("./Input_Files/cabin_branch_basin.shp"))
cabin_branch <- st_transform(cabin_branch, 2248)

crystal_rock <- st_read(file.path("./Input_Files/crystal_rock_basin.shp"))
crystal_rock <- st_transform(crystal_rock, 2248)

crystal_rock <- st_buffer(crystal_rock, dist = 0)

soper_branch <- st_read(file.path("./Input_Files/soper_branch_basin.shp"))
soper_branch <- st_transform(soper_branch, 2248)


```

# Function to join BMP info, deliniation, and landcover information

```{r}
preparing_datasets <- function(stormwater_dataset, delinate_ds, lulc_ds, year, site_name){
  

  lulc_ds <- lulc_ds %>%
    select(Id, gridcode, geometry)
  
  site_delinate_info <- cbind(stormwater_dataset, delinate_ds)
  
  new_poly <- st_as_sf(as.data.frame(site_delinate_info)[,c(1:36,38)]) 
  
  lulc_year_ds <- st_intersection(new_poly, lulc_ds)

  lulc_year_ds <- lulc_year_ds %>%
    mutate(land_cover_area = st_area(lulc_year_ds[,39]))

  lulc_year_ds_wide <- pivot_wider(as.data.frame(lulc_year_ds), names_from = gridcode.1, values_from = land_cover_area)
  
  lulc_summarize <- lulc_year_ds_wide%>%
  group_by(ASSET) %>%
  summarize(lulc_70 = ifelse("70" %in% colnames(lulc_year_ds_wide), sum(`70`, na.rm = TRUE), 0),
            lulc_80 = ifelse("80" %in% colnames(lulc_year_ds_wide), sum(`80`, na.rm = TRUE), 0),
            lulc_40 = ifelse("40" %in% colnames(lulc_year_ds_wide), sum(`40`, na.rm = TRUE), 0),
            lulc_30 = ifelse("30" %in% colnames(lulc_year_ds_wide), sum(`30`, na.rm = TRUE), 0),
            lulc_20 = ifelse("20" %in% colnames(lulc_year_ds_wide), sum(`20`, na.rm = TRUE), 0),
            lulc_90 = ifelse("90" %in% colnames(lulc_year_ds_wide), sum(`90`, na.rm = TRUE), 0),
            lulc_10 = ifelse("10" %in% colnames(lulc_year_ds_wide), sum(`10`, na.rm = TRUE), 0),
            lulc_60 = ifelse("60" %in% colnames(lulc_year_ds_wide), sum(`60`, na.rm = TRUE), 0),
            lulc_50 = ifelse("50" %in% colnames(lulc_year_ds_wide), sum(`50`, na.rm = TRUE), 0),
            lulc_0 = ifelse("0" %in% colnames(lulc_year_ds_wide), sum(`0`, na.rm = TRUE), 0),
            lulc_255 = ifelse("255" %in% colnames(lulc_year_ds_wide), sum(`255`, na.rm = TRUE), 0),
            lulc_127 = ifelse("127" %in% colnames(lulc_year_ds_wide), sum(`127`, na.rm = TRUE), 0)) %>%
  mutate(year = year, 
         lulc_70 = (lulc_70+lulc_80+lulc_60+lulc_50), 
         site = site_name, 
         lulc_20 = (lulc_20 + lulc_10), 
         lulc_40 = (lulc_40 + lulc_90),
         lulc_unknown = (lulc_0 + lulc_255 + lulc_127)) %>%
    select(-c(lulc_10, lulc_80, lulc_90, lulc_60, lulc_50, lulc_0, lulc_255, lulc_127))%>%
    ungroup()
  
  
  deliniate_info_full <- as.data.frame(full_join(as.data.frame(site_delinate_info)[1:31], lulc_summarize))
 
  
  write.csv(deliniate_info_full, file = paste0("./Output_for_Files/deliniate_lulc_info_", site_name,"_", year, ".csv"))
  
}


```



# Using function to join datasets for each site and year

```{r}

preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2010, "2010", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2011, "2011", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2012, "2012", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2013, "2013", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2014, "2014", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2015, "2015", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2016, "2016", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2017, "2017", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2018, "2018", "cr")
preparing_datasets(stormwater_cr, cr_bmp_deliniated, lulc_2019, "2019", "cr")


preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2010, "2010", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2011, "2011", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2012, "2012", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2013, "2013", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2014, "2014", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2015, "2015", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2016, "2016", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2017, "2017", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2018, "2018", "cb")
preparing_datasets(stormwater_cb, cb_bmp_deliniated, lulc_2019, "2019", "cb")


preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2010, "2010", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2011, "2011", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2012, "2012", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2013, "2013", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2014, "2014", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2015, "2015", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2016, "2016", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2017, "2017", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2018, "2018", "sb")
preparing_datasets(stormwater_sb, sb_bmp_deliniated, lulc_2019, "2019", "sb")


preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2010, "2010", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2011, "2011", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2012, "2012", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2013, "2013", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2014, "2014", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2015, "2015", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2016, "2016", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2017, "2017", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2018, "2018", "tr109")
preparing_datasets(stormwater_tr109, tr109_bmp_deliniated, lulc_2019, "2019", "tr109")


preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2010, "2010", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2011, "2011", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2012, "2012", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2013, "2013", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2014, "2014", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2015, "2015", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2016, "2016", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2017, "2017", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2018, "2018", "tr104")
preparing_datasets(stormwater_tr104, tr104_bmp_deliniated, lulc_2019, "2019", "tr104")


```

# LULC Basin Wide

```{r}

lulc_2010_cb <- st_intersection(lulc_2010, cabin_branch) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2010")

lulc_2011_cb <- st_intersection(lulc_2011, cabin_branch) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2011")

lulc_2012_cb <- st_intersection(lulc_2012, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2012")

lulc_2013_cb <- st_intersection(lulc_2013, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2013")

lulc_2014_cb <- st_intersection(lulc_2014, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2014")

lulc_2015_cb <- st_intersection(lulc_2015, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2015")

lulc_2016_cb <- st_intersection(lulc_2016, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2016")

lulc_2017_cb <- st_intersection(lulc_2017, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2017")

lulc_2018_cb <- st_intersection(lulc_2018, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2018")

lulc_2019_cb <- st_intersection(lulc_2019, cabin_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cb", year = "2019")


lulc_cb_full <- rbind(lulc_2010_cb, lulc_2011_cb, lulc_2012_cb, lulc_2013_cb, lulc_2014_cb, lulc_2015_cb, lulc_2016_cb, lulc_2017_cb, lulc_2018_cb, lulc_2019_cb)

lulc_cb_full <- lulc_cb_full %>%
  mutate(area = st_area(geometry))
lulc_cb_full <- as.data.frame(lulc_cb_full) %>%
  select(area, site_name, year, gridcode) %>%
  group_by(site_name, year, gridcode) %>%
  summarize(total_area = sum(area))



lulc_2010_tr109 <- st_intersection(lulc_2010, tr109) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2010")

lulc_2011_tr109 <- st_intersection(lulc_2011, tr109) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2011")

lulc_2012_tr109 <- st_intersection(lulc_2012, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2012")

lulc_2013_tr109 <- st_intersection(lulc_2013, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2013")

lulc_2014_tr109 <- st_intersection(lulc_2014, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2014")

lulc_2015_tr109 <- st_intersection(lulc_2015, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2015")

lulc_2016_tr109 <- st_intersection(lulc_2016, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2016")

lulc_2017_tr109 <- st_intersection(lulc_2017, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2017")

lulc_2018_tr109 <- st_intersection(lulc_2018, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2018")

lulc_2019_tr109 <- st_intersection(lulc_2019, tr109)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr109", year = "2019")


lulc_tr109_full <- rbind(lulc_2010_tr109, lulc_2011_tr109, lulc_2012_tr109, lulc_2013_tr109, lulc_2014_tr109, lulc_2015_tr109, lulc_2016_tr109, lulc_2017_tr109, lulc_2018_tr109, lulc_2019_tr109)

lulc_tr109_full <- lulc_tr109_full %>%
  mutate(area = st_area(geometry))
lulc_tr109_full <- as.data.frame(lulc_tr109_full) %>%
  select(area, site_name, year, gridcode) %>%
  group_by(site_name, year, gridcode) %>%
  summarize(total_area = sum(area))


lulc_2010_tr104 <- st_intersection(lulc_2010, tr104) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2010")

lulc_2011_tr104 <- st_intersection(lulc_2011, tr104) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2011")

lulc_2012_tr104 <- st_intersection(lulc_2012, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2012")

lulc_2013_tr104 <- st_intersection(lulc_2013, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2013")

lulc_2014_tr104 <- st_intersection(lulc_2014, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2014")

lulc_2015_tr104 <- st_intersection(lulc_2015, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2015")

lulc_2016_tr104 <- st_intersection(lulc_2016, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2016")

lulc_2017_tr104 <- st_intersection(lulc_2017, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2017")

lulc_2018_tr104 <- st_intersection(lulc_2018, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2018")

lulc_2019_tr104 <- st_intersection(lulc_2019, tr104)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "tr104", year = "2019")


lulc_tr104_full <- rbind(lulc_2010_tr104, lulc_2011_tr104, lulc_2012_tr104, lulc_2013_tr104, lulc_2014_tr104, lulc_2015_tr104, lulc_2016_tr104, lulc_2017_tr104, lulc_2018_tr104, lulc_2019_tr104)

lulc_tr104_full <- lulc_tr104_full %>%
  mutate(area = st_area(geometry))
lulc_tr104_full <- as.data.frame(lulc_tr104_full) %>%
  select(area, site_name, year, gridcode) %>%
  group_by(site_name, year, gridcode) %>%
  summarize(total_area = sum(area))


lulc_2010_cr <- st_intersection(lulc_2010, crystal_rock) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2010")

lulc_2011_cr <- st_intersection(lulc_2011, crystal_rock) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2011")

lulc_2012_cr <- st_intersection(lulc_2012, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2012")

lulc_2013_cr <- st_intersection(lulc_2013, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2013")

lulc_2014_cr <- st_intersection(lulc_2014, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2014")

lulc_2015_cr <- st_intersection(lulc_2015, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2015")

lulc_2016_cr <- st_intersection(lulc_2016, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2016")

lulc_2017_cr <- st_intersection(lulc_2017, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2017")

lulc_2018_cr <- st_intersection(lulc_2018, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2018")

lulc_2019_cr <- st_intersection(lulc_2019, crystal_rock)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "cr", year = "2019")


lulc_cr_full <- rbind(lulc_2010_cr, lulc_2011_cr, lulc_2012_cr, lulc_2013_cr, lulc_2014_cr, lulc_2015_cr, lulc_2016_cr, lulc_2017_cr, lulc_2018_cr, lulc_2019_cr)

lulc_cr_full <- lulc_cr_full %>%
  mutate(area = st_area(geometry))
lulc_cr_full <- as.data.frame(lulc_cr_full) %>%
  select(area, site_name, year, gridcode) %>%
  group_by(site_name, year, gridcode) %>%
  summarize(total_area = sum(area))


lulc_2010_sb <- st_intersection(lulc_2010, soper_branch) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2010")

lulc_2011_sb <- st_intersection(lulc_2011, soper_branch) %>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2011")

lulc_2012_sb <- st_intersection(lulc_2012, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2012")

lulc_2013_sb <- st_intersection(lulc_2013, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2013")

lulc_2014_sb <- st_intersection(lulc_2014, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2014")

lulc_2015_sb <- st_intersection(lulc_2015, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2015")

lulc_2016_sb <- st_intersection(lulc_2016, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2016")

lulc_2017_sb <- st_intersection(lulc_2017, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2017")

lulc_2018_sb <- st_intersection(lulc_2018, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2018")

lulc_2019_sb <- st_intersection(lulc_2019, soper_branch)%>%
  select(Id, gridcode, geometry)%>%
  mutate(site_name = "sb", year = "2019")


lulc_sb_full <- rbind(lulc_2010_sb, lulc_2011_sb, lulc_2012_sb, lulc_2013_sb, lulc_2014_sb, lulc_2015_sb, lulc_2016_sb, lulc_2017_sb, lulc_2018_sb, lulc_2019_sb)

lulc_sb_full <- lulc_sb_full %>%
  mutate(area = st_area(geometry))
lulc_sb_full <- as.data.frame(lulc_sb_full) %>%
  select(area, site_name, year, gridcode) %>%
  group_by(site_name, year, gridcode) %>%
  summarize(total_area = sum(area))


lulc_all_basins <- rbind(lulc_sb_full, lulc_cr_full, lulc_cb_full, lulc_tr104_full, lulc_tr109_full)

lulc_all_basins_edit <- lulc_all_basins %>%
  group_by(site_name, year)%>%
  mutate(area_whole_basin = sum(total_area, na.rm = T))%>%
  mutate(percent_lulc = as.numeric((total_area/area_whole_basin)*100), 
         year = as.numeric(year), gridcode = as.factor(gridcode))%>%
  mutate(updated_gridcode = case_when(gridcode == "20"~ "20",
                                      gridcode == "10"~ "20",
                                      gridcode == "30"~ "30", 
                                      gridcode == "40"~ "40", 
                                      gridcode == "90"~ "40",
                                      gridcode == "70"~ "70",
                                      gridcode == "80"~ "70",
                                      gridcode == "60"~ "70",
                                      gridcode == "50"~ "70",
                                      gridcode == "0"~ "unknown",
                                      gridcode == "225"~ "unknown",
                                      gridcode == "127"~ "unknown"))

lulc_all_basins_final <- lulc_all_basins_edit %>%
  group_by(year, site_name, updated_gridcode)%>%
  summarize(total_area = sum(total_area)) %>%
  ungroup()%>%
  group_by(site_name, year)%>%
  mutate(area_whole_basin = sum(total_area, na.rm = T))%>%
  mutate(percent_lulc = as.numeric((total_area/area_whole_basin)*100))

write.csv(lulc_all_basins_final, file = "./Output_for_Files/lulc_for_full_basins.csv")



```


# TR109 Summaries Yearly

```{r}

deliniate_lulc_info_tr109_2019 <- read_csv("./Output_for_Files/deliniate_lulc_info_tr109_2019.csv") 
deliniate_lulc_info_tr104_2019 <- read_csv("./Output_for_Files/deliniate_lulc_info_tr104_2019.csv") 
deliniate_lulc_info_cb_2019 <- read_csv("./Output_for_Files/deliniate_lulc_info_cb_2019.csv") 
deliniate_lulc_info_cr_2019 <- read_csv("./Output_for_Files/deliniate_lulc_info_cr_2019.csv") 
deliniate_lulc_info_sb_2019 <- read_csv("./Output_for_Files/deliniate_lulc_info_sb_2019.csv") 


yearly_summary_lulc <- function(site_bmp_deliniated, deliniated_lulc_site_2019, bmp_full_ds, filter_date, lulc_year, site_outline, site_name, year){
 
  site_for_summary_ds <-cbind(site_bmp_deliniated, deliniated_lulc_site_2019)
  
  site_for_summary_ds <- site_for_summary_ds %>%
  dplyr::mutate(FINAL_DATE = as.Date(FINAL_DATE, format = "%m/%d/%Y"))%>%
  filter(FINAL_DATE < filter_date )
  
  site_for_summary <- st_union(site_for_summary_ds)
  
  site_lulc_year_whole <- st_intersection(lulc_year, site_outline)
  
  site_lulc_year <- st_difference(site_lulc_year_whole, site_for_summary)
  
  site_lulc_year <- st_union(site_lulc_year)

  site_lulc_year <- st_difference(site_lulc_year_whole, site_lulc_year)

  site_lulc_year$area <- st_area(site_lulc_year)
  
  site_lulc_year_summary <-as.data.frame(site_lulc_year) %>%
  group_by(gridcode)%>%
  dplyr::summarize(lulc_area = sum(area))%>%
  dplyr::mutate(site = site_name, year = year)%>%
  dplyr::select(gridcode, lulc_area, site, year)

site_lulc_year_summary <- site_lulc_year_summary %>%
  dplyr::mutate(storage = sum(site_for_summary_ds$Stores_cf, na.rm = T))

return(site_lulc_year_summary)


}


tr109_2010 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2011-01-01" ,
                    lulc_year = lulc_2010,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2010")

tr109_2011 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2012-01-01" ,
                    lulc_year = lulc_2011,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2011")

tr109_2012 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2013-01-01" ,
                    lulc_year = lulc_2012,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2012")

tr109_2013 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2014-01-01" ,
                    lulc_year = lulc_2013,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2013")

tr109_2014 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2015-01-01" ,
                    lulc_year = lulc_2014,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2014")

tr109_2015 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2016-01-01" ,
                    lulc_year = lulc_2015,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2015")

tr109_2016 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2017-01-01" ,
                    lulc_year = lulc_2016,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2016")

tr109_2017 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2018-01-01" ,
                    lulc_year = lulc_2017,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2017")

tr109_2018 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2019-01-01" ,
                    lulc_year = lulc_2018,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2018")

tr109_2019 <- yearly_summary_lulc(site_bmp_deliniated = tr109_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr109_2019,
                    filter_date = "2020-01-01" ,
                    lulc_year = lulc_2019,
                    site_outline = tr109,
                    site_name = "tr109",
                    year = "2019")

all_bmp_tr109_lulc_storage__yearly_summaries <- rbind.fill(tr109_2019, tr109_2018, tr109_2017, tr109_2016, tr109_2015, tr109_2014, tr109_2013, tr109_2012, tr109_2011, tr109_2010)

all_bmp_tr109_lulc_storage__yearly_summaries <- all_bmp_tr109_lulc_storage__yearly_summaries %>%
  dplyr::mutate(gridcode = case_when(gridcode == 20 ~ "treated_20", gridcode == 30 ~ "treated_30", gridcode == 40 ~ "treated_40", gridcode == 70 ~ "treated_70"))

all_bmp_tr109_lulc_storage__yearly_summaries <- pivot_wider(all_bmp_tr109_lulc_storage__yearly_summaries, names_from = gridcode, values_from = lulc_area)



```
# TR-104 Summaries Yearly
```{r}


tr104_2010 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2011-01-01" ,
                    lulc_year = lulc_2010,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2010")

tr104_2011 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2012-01-01" ,
                    lulc_year = lulc_2011,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2011")

tr104_2012 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2013-01-01" ,
                    lulc_year = lulc_2012,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2012")

tr104_2013 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2014-01-01" ,
                    lulc_year = lulc_2013,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2013")

tr104_2014 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2015-01-01" ,
                    lulc_year = lulc_2014,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2014")

tr104_2015 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2016-01-01" ,
                    lulc_year = lulc_2015,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2015")

tr104_2016 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2017-01-01" ,
                    lulc_year = lulc_2016,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2016")

tr104_2017 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2018-01-01" ,
                    lulc_year = lulc_2017,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2017")

tr104_2018 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2019-01-01" ,
                    lulc_year = lulc_2018,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2018")

tr104_2019 <- yearly_summary_lulc(site_bmp_deliniated = tr104_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_tr104_2019,
                    filter_date = "2020-01-01" ,
                    lulc_year = lulc_2019,
                    site_outline = tr104,
                    site_name = "tr104",
                    year = "2019")

all_bmp_tr104_lulc_storage__yearly_summaries <- rbind.fill(tr104_2019, tr104_2018, tr104_2017, tr104_2016, tr104_2015, tr104_2014, tr104_2013, tr104_2012, tr104_2011, tr104_2010)

all_bmp_tr104_lulc_storage__yearly_summaries <- all_bmp_tr104_lulc_storage__yearly_summaries %>%
  dplyr::mutate(gridcode = case_when(gridcode == 20 ~ "treated_20", gridcode == 30 ~ "treated_30", gridcode == 40 ~ "treated_40", gridcode == 70 ~ "treated_70"))

all_bmp_tr104_lulc_storage__yearly_summaries <- pivot_wider(all_bmp_tr104_lulc_storage__yearly_summaries, names_from = gridcode, values_from = lulc_area)

```
# Cabin Branch Summaries Yearly

```{r}



cb_2017 <- yearly_summary_lulc(site_bmp_deliniated = cb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2018-01-01" ,
                    lulc_year = lulc_2017,
                    site_outline = cabin_branch,
                    site_name = "cb",
                    year = "2017")

cb_2018 <- yearly_summary_lulc(site_bmp_deliniated = cb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2019-01-01" ,
                    lulc_year = lulc_2018,
                    site_outline = cabin_branch,
                    site_name = "cb",
                    year = "2018")

cb_2019 <- yearly_summary_lulc(site_bmp_deliniated = cb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2020-01-01" ,
                    lulc_year = lulc_2019,
                    site_outline = cabin_branch,
                    site_name = "cb",
                    year = "2019")

all_bmp_cb_lulc_storage__yearly_summaries <- rbind.fill(cb_2019, cb_2018, cb_2017)

all_bmp_cb_lulc_storage__yearly_summaries <- all_bmp_cb_lulc_storage__yearly_summaries %>%
  dplyr::mutate(gridcode = case_when(gridcode == 20 ~ "treated_20", gridcode == 30 ~ "treated_30", gridcode == 40 ~ "treated_40", gridcode == 70 ~ "treated_70"))

all_bmp_cb_lulc_storage__yearly_summaries <- pivot_wider(all_bmp_cb_lulc_storage__yearly_summaries, names_from = gridcode, values_from = lulc_area)

```

# Crystal Rock Summaries Yearly

```{r}

cr_2010 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2011-01-01" ,
                    lulc_year = lulc_2010,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2010")

cr_2011 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2012-01-01" ,
                    lulc_year = lulc_2011,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2011")

cr_2012 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2013-01-01" ,
                    lulc_year = lulc_2012,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2012")

cr_2013 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2014-01-01" ,
                    lulc_year = lulc_2013,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2013")

cr_2014 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2015-01-01" ,
                    lulc_year = lulc_2014,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2014")

cr_2015 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2016-01-01" ,
                    lulc_year = lulc_2015,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2015")

cr_2016 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2017-01-01" ,
                    lulc_year = lulc_2016,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2016")

cr_2017 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2018-01-01" ,
                    lulc_year = lulc_2017,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2017")

cr_2018 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2019-01-01" ,
                    lulc_year = lulc_2018,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2018")

cr_2019 <- yearly_summary_lulc(site_bmp_deliniated = cr_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_cr_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2020-01-01" ,
                    lulc_year = lulc_2019,
                    site_outline = crystal_rock,
                    site_name = "cr",
                    year = "2019")

all_bmp_cr_lulc_storage__yearly_summaries <- rbind.fill(cr_2019, cr_2018, cr_2017, cr_2016, cr_2015, cr_2014, cr_2013, cr_2012, cr_2011, cr_2010)

all_bmp_cr_lulc_storage__yearly_summaries <- all_bmp_cr_lulc_storage__yearly_summaries %>%
  dplyr::mutate(gridcode = case_when(gridcode == 20 ~ "treated_20", gridcode == 30 ~ "treated_30", gridcode == 40 ~ "treated_40", gridcode == 70 ~ "treated_70"))



all_bmp_cr_lulc_storage__yearly_summaries <- pivot_wider(all_bmp_cr_lulc_storage__yearly_summaries, names_from = gridcode, values_from = lulc_area)

```

# Soper Branch Summaries Yearly

```{r}


sb_2010 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2011-01-01" ,
                    lulc_year = lulc_2010,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2010")

sb_2011 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2012-01-01" ,
                    lulc_year = lulc_2011,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2011")

sb_2012 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2013-01-01" ,
                    lulc_year = lulc_2012,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2012")

sb_2013 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2014-01-01" ,
                    lulc_year = lulc_2013,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2013")

sb_2014 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2015-01-01" ,
                    lulc_year = lulc_2014,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2014")

sb_2015 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2016-01-01" ,
                    lulc_year = lulc_2015,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2015")

sb_2016 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2017-01-01" ,
                    lulc_year = lulc_2016,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2016")

sb_2017 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2018-01-01" ,
                    lulc_year = lulc_2017,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2017")

sb_2018 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2019-01-01" ,
                    lulc_year = lulc_2018,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2018")

sb_2019 <- yearly_summary_lulc(site_bmp_deliniated = sb_bmp_deliniated, 
                    deliniated_lulc_site_2019 = deliniate_lulc_info_sb_2019,
                    bmp_full_ds = bmp_full,
                    filter_date = "2020-01-01" ,
                    lulc_year = lulc_2019,
                    site_outline = soper_branch,
                    site_name = "sb",
                    year = "2019")

all_bmp_sb_lulc_storage__yearly_summaries <- rbind.fill(sb_2019, sb_2018, sb_2017, sb_2016, sb_2015, sb_2014, sb_2013, sb_2012, sb_2011, sb_2010)

all_bmp_sb_lulc_storage__yearly_summaries <- all_bmp_sb_lulc_storage__yearly_summaries %>%
  dplyr::mutate(gridcode = case_when(gridcode == 20 ~ "treated_20", gridcode == 30 ~ "treated_30", gridcode == 40 ~ "treated_40", gridcode == 70 ~ "treated_70"))

all_bmp_sb_lulc_storage__yearly_summaries <- pivot_wider(all_bmp_sb_lulc_storage__yearly_summaries, names_from = gridcode, values_from = lulc_area)


```

```{r}
library(units)

all_bmp_all_sites_lulc_storage_yearly_summaries <- rbind.fill(all_bmp_cb_lulc_storage__yearly_summaries, all_bmp_cr_lulc_storage__yearly_summaries, all_bmp_sb_lulc_storage__yearly_summaries, all_bmp_tr104_lulc_storage__yearly_summaries, all_bmp_tr109_lulc_storage__yearly_summaries)



lulc_for_full_basins <- read_csv("Output_for_Files/lulc_for_full_basins.csv")

lulc_for_full_basins <- lulc_for_full_basins %>%
  select(-c(percent_lulc, `...1`))%>%
  mutate(year = as.character(year))

lulc_for_full_basins <- pivot_wider(lulc_for_full_basins, names_from = updated_gridcode, values_from = total_area)

colnames(lulc_for_full_basins) <- c("year", "site", "total_basin_area", "total_basin_20", "total_basin_30", "total_basin_40", "total_basin_70")

all_bmp_all_sites_lulc_storage_yearly_summaries <- left_join(all_bmp_all_sites_lulc_storage_yearly_summaries, lulc_for_full_basins, by = c("year", "site"))
  
all_bmp_all_sites_lulc_storage_yearly_summaries<- all_bmp_all_sites_lulc_storage_yearly_summaries%>%
  dplyr::mutate(percent_20_treated = (treated_20/total_basin_20)*100, untreated_20 = (total_basin_20 -drop_units(treated_20)),
         percent_30_treated = (treated_30/total_basin_30)*100, untreated_30 = (total_basin_30 - drop_units(treated_20)),
         percent_40_treated = (treated_40/total_basin_40)*100, untreated_40 = (total_basin_40 - drop_units(treated_20)),
         percent_70_treated = (treated_70/total_basin_70)*100, untreated_70 = (total_basin_70 - drop_units(treated_20)))

write.csv(all_bmp_all_sites_lulc_storage_yearly_summaries, file = "./Output_for_Files/all_bmp_type_yearly_summary.csv")

all_bmp_type_yearly_summary <-all_bmp_all_sites_lulc_storage_yearly_summaries

```


# Yearly Storage Dataset (more data points without lulc restrictions)

```{r}


stores_by_year <- function(site_ds, Site){
  
  full_storage <- tibble()
  
    list_year <- c("2007-01-01", "2008-01-01","2009-01-01","2010-01-01","2011-01-01","2012-01-01","2013-01-01","2014-01-01","2015-01-01","2016-01-01","2017-01-01","2018-01-01","2019-01-01","2020-01-01","2021-01-01")
    
    just_year <- year(list_year)-1
  
  for (i in 1:length(list_year)) {

    
    site_ds_yearly <- site_ds %>%
      filter(FINAL_DATE < list_year[i]) %>%
      summarize(total_storage = sum(as.numeric(Stores_cf), na.rm = TRUE)) %>%
      mutate(year = just_year[i], Site = Site)
      
      full_storage <- rbind(full_storage, site_ds_yearly)
    
  }
    
    write.csv(full_storage, file = paste0("./Output_for_Files/full_storage", Site, ".csv"))
  
}


stores_by_year(site_ds = tr109_full_ds_stores, Site = "TR109")
stores_by_year(site_ds = tr104_full_ds_stores, Site = "TR104")
stores_by_year(site_ds = cb_full_ds_stores, Site = "CB")
stores_by_year(site_ds = cr_full_ds_stores, Site = "CR")
stores_by_year(site_ds = sb_full_ds_stores, Site = "SB")


full_storage_tr109 <- read.csv("./Output_for_Files/full_storageTR109.csv")
full_storage_tr104 <- read.csv("./Output_for_Files/full_storageTR104.csv")
full_storage_cb <- read.csv("./Output_for_Files/full_storageCB.csv")
full_storage_cr <- read.csv("./Output_for_Files/full_storageCR.csv")
full_storage_sb <- read.csv("./Output_for_Files/full_storageSB.csv")

```


# Variables for context for deliniated lulc

```{r}

sem_vars_and_precip <- read.csv("./Input_Files/SEM_PRECIP_2022.CSV")

land_use_storage_summarized <- read.csv("./Output_for_Files/land_use_storage_summary_by_site_year.csv")

lulc_all_basins <- read.csv("./Output_for_Files/lulc_for_full_basins.csv")

land_use_storage_summarized <- land_use_storage_summarized[,2:7] %>%
  mutate(Site = toupper(site), Year = year)

lulc_all_basins <- lulc_all_basins[,2:7]

lulc_all_basins_wider <- pivot_wider(lulc_all_basins, names_from = updated_gridcode, values_from = c(total_area, percent_lulc)) %>%
  mutate(Site = toupper(site_name))%>%
  dplyr::select(-c(percent_lulc_20,percent_lulc_30,percent_lulc_40,percent_lulc_70))


sem_lulc_storage <- left_join(sem_vars_and_precip, land_use_storage_summarized)


sem_lulc_storage_more_info <- left_join(sem_lulc_storage, lulc_all_basins_wider)

sem_lulc_storage_more_info <- sem_lulc_storage_more_info %>%
  mutate(percent_of_all_70 = (lulc_70/total_area_70)*100, 
         percent_of_all_30 = (lulc_30/total_area_30)*100,
         percent_of_all_40 = (lulc_40/total_area_40)*100,
         percent_of_all_20 = (lulc_20/total_area_20)*100,
         percent_70_whole_basin = (lulc_70/area_whole_basin)*100,
         percent_40_whole_basin = (lulc_40/area_whole_basin)*100,
         percent_30_whole_basin = (lulc_30/area_whole_basin)*100,
         percent_20_whole_basin = (lulc_20/area_whole_basin)*100,
         PH = as.numeric(PH),
         CONDUCT = as.numeric(CONDUCT),
         AIRTEMP = as.numeric(AIRTEMP),
         H2OTEMP_C = as.numeric(H2OTEMP_C),
         DISOXY = as.numeric(DISOXY))

write.csv(sem_lulc_storage_more_info, file = "./Output_for_Files/sem_lulc_storage_more_info.csv")

```